---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# trendEcon data repository

We construct economic indicators for Switzerland, based on Google Trends data.

The data is displayed and described at: https://www.trendecon.org


### Data

The data is stored as CSV in the [`data`](https://github.com/trendecon/data/tree/master/data) folder:

| Description              | Switzerland                                                                                               | Germany                                                                                                     | Austria                                                                                                     |
|--------------------------|-----------------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------|-------------------------------------------------------------------------------------------------------------|
| clothing                 | [clothing_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/clothing_sa.csv)         | ---                                                                                                         | ---                                                                                                         |
| food delivery            | [fooddelivery_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/fooddelivery_sa.csv) | ---                                                                                                         | ---                                                                                                         |
| garden                   | [garden_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/garden_sa.csv)             | ---                                                                                                         | ---                                                                                                         |
| home office equipment    | [homeoffice_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/homeoffice_sa.csv)     | ---                                                                                                         | ---                                                                                                         |
| luxury                   | [luxury_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/luxury_sa.csv)             | ---                                                                                                         | ---                                                                                                         |
| mobility                 | [mobility_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/mobility_sa.csv)         | ---                                                                                                         | ---                                                                                                         |
| social                   | [social_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/social_sa.csv)             | ---                                                                                                         | ---                                                                                                         |
| travel                   | [travel_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/travel_sa.csv)             | ---                                                                                                         | ---                                                                                                         |
| trendecon main indicator | [trendecon_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/ch/trendecon_sa.csv)       | [trendecon_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/de/trendecon_sa.csv)         | [trendecon_sa.csv](https://raw.githubusercontent.com/trendecon/data/master/raw/at/trendecon_sa.csv)         |


### Example

The following R code download and displays the main indicator for CH, DE, ant AT:

```{r example, fig.height=3, fig.width=8}

data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/ch/trendecon_sa.csv")
tsbox::ts_plot(data, title = "Switzerland")

data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/de/trendecon_sa.csv")
tsbox::ts_plot(data, title = "Germany")

data <- read.csv("https://raw.githubusercontent.com/trendecon/data/master/data/at/trendecon_sa.csv")
tsbox::ts_plot(data, title = "Austria")

```

